% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca (fork 1)
% (c) 2016 Ananda Seelan <ananda.seelan@gmail.com> (fork 2)
% (c) 2024 Ariharasudhan <aravindariharan@gmail.com> https://arihara-sudhan.github.io (fork 3)
% Licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License.

\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%-----------------------------------------------------------
% Margin setup
\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{9.5in} % Removed redundant definition
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

% Packages
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lmodern}
\usepackage{url} % Added for better URL formatting

\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\textbf{\sffamily{\mbox{~}{\large #1} \vphantom{p\^{E}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-4pt}} % Reduced spacing from -6pt to -4pt for better alignment

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

%-----------------------------------------------------------
% Fancy footer settings
\pagestyle{fancy}
\fancyhead{} % Clear all header fields
\renewcommand{\headrulewidth}{0pt} % No line in header area
\fancyfoot{} % Clear all footer fields
\fancyfoot[LE,RO]{\thepage} % Page number in "outer" position of footer
\fancyfoot[RE,LO]{\fontsize{9}{6}\selectfont Ariharasudhan - Resume} % Increased footer text size

%-----------------------------------------------------------
\begin{document}

% Contact Information
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Ariharasudhan}  & +91 6382509390\\
\url{https://arihara-sudhan.github.io} &  aravindariharan@gmail.com \\ % Used \url{} for better line-breaking
\end{tabular*}
\\
\vspace{0.05in}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\vspace{0.025in}

%-----------------------------------------------------------
% Education
\resheading{Education}
\begin{itemize}
\item[]
    \ressubheading{Einstein College of Engineering}{Tirunelveli, India}{B.E., Computer Science and Engineering (CGPA: 8.83)}{2019 - 2023}

\item[]
    \ressubheading{Government Hr. Sec. School}{Tenkasi, India}{Higher Secondary School Examination (Score: 87\%)}{2019}
\end{itemize}

%-----------------------------------------------------------
% Programming Skills
\resheading{Programming Skills}
\vspace{-2mm}
\begin{itemize}
\item[]{\textit{Deep Learning Frameworks:} PyTorch, NumPy}\vspace{-2mm}
\item[]{\textit{Languages:} Python, Java, JavaScript, C}\vspace{-2mm}
\item[]{\textit{Databases:} MySQL, MongoDB}\vspace{-2mm}
\item[]{\textit{Web Development Frameworks:} FastAPI, ReactJS, NodeJS, Express.js}\vspace{-2mm}
\item[]{\textit{Operating Systems:} Windows, macOS, Linux (mainly Ubuntu)}\vspace{-2mm}
\item[]{\textit{Version Control Systems:} Git}\vspace{-2mm}
\end{itemize}

%-----------------------------------------------------------
% Work Experience
\resheading{Work Experience}
\begin{itemize}
\item[]
    \ressubheading{Moative}{Chennai, India}{AI/ML Engineer}{June 2025 - Present}
    \begin{itemize}
        \resitem{Building and maintaining fullstack AI systems from model development to deployment}
        \resitem{Deploying services on AWS EC2, developing LLM-powered dashboards, and working on Agentic AI using Google's Gemini API}
    \end{itemize}
\item[]
    \ressubheading{Zoho Corporation}{Tenkasi, India}{Member Technical Staff, Zoho Desk}{April 2024 - May 2025}
    \begin{itemize}
        \resitem{Developing UI and AI systems for Zoho Desk.}
        \resitem{\textit{Currently working on a Retrieval-Augmented Generation (RAG) system using FAISS for document retrieval and a HuggingFace LLM for improved responses. Also developing production-grade JavaScript and ReactJS features.}}
    \end{itemize}
\item[]
	\ressubheading{Zoho Corporation}{Trichy, India}{Member Technical Staff, ZLabs Speech Profiling}{Jan 2024 - April 2024}
	\begin{itemize}
		\resitem{Learned about Audio Feature Extraction}
		\resitem{\textit{I conducted audio classification using CNNs, achieving peak accuracy. I addressed challenges with varying sampling rates and gained valuable insights into audio engineering and feature extraction.}}
	\end{itemize}
	
\item[]
	\ressubheading{Zoho Corporation}{Tripur, India}{Member Technical Staff, ZLabs Intelligent Document Processing}{Jun 2023 - Dec 2023}
	\begin{itemize}
		\resitem{Developed A Fewshot Doc2Vec Model}
		\resitem{\textit{I began my research with ResNet-50 and then transitioned to DiT, a vision transformer pretrained on a document dataset. We extracted document embeddings and performed few-shot training using Triplet Loss. With well-labeled data, we achieved a similarity search accuracy of 100\%. Later, in my research, I discovered interesting insights, such as classification models sometimes performing like few-shot models and vice versa. Finally, I conducted multimodal training by combining visual features from ResNet and textual features from BERT, resulting in strong generalization.}}
	\end{itemize}

\item[]
	\ressubheading{Zoho Corporation}{Coimbatore, India}{Project Trainee, ZLabs Intelligent Document Processing}{Jan 2023 - Jun 2023}
	\begin{itemize}
		\resitem{Learned Deep Learning Computer Hardwares, Backend Frameworks and Revised Python}
		\resitem{\textit{I meticulously learned deep learning, which sparked my interest in creating small books (https://arihara-sudhan.github.io/books). I successfully trained small neural networks and tackled a few-shot classification task, which I resolved using contrastive loss.}}
	\end{itemize}

\end{itemize}

%-----------------------------------------------------------
% Projects
\resheading{Projects}
\begin{itemize}

\item[]
	\textbf{AI Powered MediKit}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{Revolutionizes healthcare diagnostics by leveraging Vision Transformers (ViTs) for precise medical image analysis.}
		\resitem{Overcomes CNN limitations by capturing fine-grained medical features with superior accuracy.}
		\resitem{Features Heartbeat Analysis using Mel-Frequency Cepstral Coefficients (MFCC) to classify heartbeats and detect abnormalities.}
		\resitem{Supports few-shot classification for tablet identification, minimizing retraining needs and improving adaptability.}
		\resitem{Includes a Herbal Solution feature that bridges modern AI with traditional medicine by suggesting natural remedies.}
		\resitem{Combines precision, innovation, and accessibility to set a new benchmark in AI-driven medical solutions.}
	\end{itemize}

\item[]
	\textbf{MindKural - RAG System}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{Developed a conversational AI bot using LangChain to answer queries based on Thirukkural, the timeless Tamil literary masterpiece.}
		\resitem{Utilized FAISS for vector embeddings and similarity search to enable efficient retrieval.}
		\resitem{Enhanced responses using Retrieval-Augmented Generation (RAG) with Falcon LLM.}
		\resitem{Transformed Thirukkural’s wisdom into a knowledge framework that informs and heals.}
	\end{itemize}

\item[]
	\textbf{Grouped Detection of Objects}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{Utilized the YOLO algorithm to detect objects in images accurately.}
		\resitem{Cropped regions of interest and applied a Swin Transformer-based few-shot network for classification.}
		\resitem{Implemented K-means clustering with the Elbow Method to optimize object grouping.}
		\resitem{Deployed a scalable real-time prediction microservice using FastAPI.}
	\end{itemize}

\item[]
	\textbf{Fewshot Classify Anything Model}
	\vspace{-3mm}
	\begin{itemize}
	    \resitem{Performs similarity searches on stored embeddings of images.}
	    \resitem{Uses a Swin Transformer as the backbone and employs triplet loss for training embeddings.}
	    \resitem{Efficiently classifies new inputs by referencing a few saved embeddings in an index.}
	\end{itemize}

\item[]
	\textbf{Next-Word Prediction using Bigram Model}
	\vspace{-3mm}
	\begin{itemize}
	    \resitem{Implemented a probabilistic language model that predicts the next word based on the previous word using a bigram approach.}
	    \resitem{Utilized joint probability and conditional probability to compute word sequences.}
	    \resitem{Demonstrated real-world text generation applications by starting with seed words and generating coherent sentences.}
	\end{itemize}

\item[]
	\textbf{Dialect Classification using Naïve Bayes}
	\vspace{-3mm}
	\begin{itemize}
	    \resitem{Built a text classification model for dialect detection using the Naive Bayes algorithm.}
	    \resitem{Employed the Bag of Words approach to store word frequencies for classification.}
	    \resitem{Used Laplace Smoothing to handle zero probabilities and prevent model breakdown.}
	    \resitem{Optimized for efficiency by working in log-space to prevent underflow when multiplying small probabilities.}
	\end{itemize}

\end{itemize}

%-----------------------------------------------------------
% Achievements & Activities
\newpage
\resheading{Achievements/Activities}
\begin{itemize}
    \item Educating Peers at Zoho Desk on Client Technology  
          \textit{I mentor my team on JavaScript internals, the functional programming paradigm, ReactJS, and TypeScript.} (SEP 2024)
    \vspace{-2mm}
    
    \item Learning NLP and Speech Processing nightly at a study group meet (DAILY)
    \vspace{-2mm}

    \item Taught Basic Machine Learning to Students  
          \textit{Guided expert students from Coimbatore, Tirunelveli, and Madurai on Multi-Layer Perceptron and CNN via Google Meet.} (OCT 2024)
    \vspace{-2mm}

    \item Taught MERN Stack Development to Students  
          \textit{Conducted weekend sessions at Einstein College of Engineering on MERN Stack Development.} (DEC 2024)
    \vspace{-2mm}

    \item Session on "Meet AI" at Kamaraj College of Engineering and Technology, Virudhunagar  
          \textit{Taught AI fundamentals, fostering curiosity and learning to inspire an AI-powered South.} (JAN 2025)
    \vspace{-2mm}

    \item Session on "On Technology and Rural Development" at AKY Polytechnic College, Nellai  
          \textit{Discussed technology’s role in rural development, education, societal changes, and self-improvement.} (SEP 2024)
    \vspace{-2mm}

    \item Qualified for the final round of Medecro.ai's Hackathon  
          \textit{Developed AI-powered MediKit, a bundle of AI solutions for medical problems such as heartbeat analysis, tumor detection, and cell classification.} (AUG 2024)
    \vspace{-2mm}

    \item Qualified for the final round of the Atheneum Hackathon, IGDTUW, New Delhi  
          \textit{Proposed Smart Education System with OCR-based test evaluation, virtual pen, virtual quiz, and face recognition-based attendance.} (AUG 2022)
    \vspace{-2mm}

    \item Talent Search Examination, JP College of Engineering, Tenkasi  
          \textit{Secured 1st Prize for excellence in Mathematics and Science.} (FEB 2017)
    \vspace{-2mm}

    \item Yuva Shri Kala Bharathi Award, Bharathi Yuva Kenthra, Madurai  
          \textit{Recognized for outstanding performance in proficiency and arts.} (JAN 2018)
    \vspace{-2mm}

    \item Thirukkural Literature Explanations  
          \textit{Dedicating my evenings to writing detailed explanations for each Thirukkural.} (OCT 2024)
    \vspace{-2mm}

    \item Aladi Aruna Merit Scholarship, Einstein College of Engineering, Tirunelveli  
          \textit{Awarded a scholarship for securing a top rank in academics.} (FEB 2017)
    \vspace{-2mm}

    \item 1st Prizes in Paper Presentation, Web Designing, Code Debugging  
          \textit{Rohini College of Engineering, Kanyakumari - National Level Technical Symposium.} (MAR 2022)
    \vspace{-2mm}

    \item 1st Prizes in Paper Presentation and Web Designing Competitions  
          \textit{PSN College of Engineering, Tirunelveli - National Level Technical Symposium.} (APR 2022)
    \vspace{-2mm}

    \item 1st Prizes in Paper Presentation, Web Designing, and Technical Quiz  
          \textit{Thamirabarani Engineering College, Tirunelveli - National Level Technical Symposium.} (MAY 2022)
    \vspace{-2mm}

    \item Best Project Presentation in Mini Project Expo for III-year students  
          \textit{Developed an AI-Based Student Service System at Einstein College of Engineering.}
\end{itemize}
\vspace{2cm}
\end{document}
